Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-03-08 reply_to_reviews.R1.tex

We do not think we can provide any other proof for this. A confidence
interval and a p-value are directly related. The TOST procedure is a
test using the confidence interval, and the SGPV (now that we clearly
limited our discussion to a SGPV based on a confidence interval
calculated from continuous normal data) compared against the same
equivalence bounds will be related as we describe. But we believe our
article might not have been clear enough about that we limit our
discussion about the correspondence of the curves to these 3 points.
Indeed, in some figures, the curves are less similar (e.g., Figure 6, 9,
13). Nevertheless, in these graphs, we still have the correspondence
between these 3 points (or at leas tthe 2 points if the CI is too wide
compared to the equivalence bounds to ever observe a \emph{p} = 0.025).
To make it clearer that we talk about the overlap in these 3 critical
points, we have added:

\enquote{When we discuss the relationship between the p-values from TOST
and the SGPV, we focus on their correspondence at three values, namely
where the TOST \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} =
0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1.
These three values are important for the SGPV because they indicate the
values at which the SGPV indicates the data should be interpreted as
compatible with the null hypothesis (SGPV = 1), or with the alternative
hypothesis (SGPV = 0), or when the data are strictly inconclusive (SGPV
= 0.5). These three points of overlap are indicated by the horizontal
dotted lines in Figure 2.}

We believe this satisfactorily addresses the point by the reviewer that
\enquote{Because of this lack of discussion, the reader can easily miss
that the close correspondence only occurs when the sample size is large
enough that the standard error is very small relative to the width of
the equivalence zone.} Indeed, the correspondence between the TOST and
SGPV at these 3 points should be obvious to anyone who understands the
relationship between a p-value and a confidence interval, so we do not
provide any further proof, but we hope that clarifying we talk about the
correspondence of these 3 points, and not the entire curve, is
sufficient to address point 2.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  We are aware of the Beger and Hsu (1996) article. But if the reviewer
  reads more closely, it should be clear that we never say the TOST is
  UMP. We say that TOST is a test procedure that aims to control error
  rates - our use of the term \enquote{Neyman-Pearson perspective}
  refers to the classic difference between significance tests (Fisher)
  and hypothesis tests (Neyman-Pearson). We do not imply that any test
  that fixes an error rate is a NP test. Because many psychologists are
  not trained in the difference between a Fisherian approach and a
  Neyman Pearson approach to the use of p-values, we are simply adding a
  \enquote{Neyman-Pearson} approach in the text to explain that
  \enquote{From a Neyman-Pearson perspective on statistical inferences
  the main conclusion is based on whether or not \(p < \alpha\), and
  thus an equivalence test and SGPV can be performed by simply checking
  whether the confidence interval falls within the equivalence range,
  just as a null-hypothesis test can be performed by checking whether
  the confidence interval contains zero or not.} We believe this is a
  correct use of the term \enquote{Neyman-Pearson perspective on
  statistical inferences}.
\item
  We tried to find the passage the reviewer refers to when he writes
  \enquote{In light of this, the assertion without proof that classical
  p-values provide more or better assessments of the \enquote{evidence}
  appear out of place.} but we could not. We do not use the word
  \enquote{evidence} in the text (because neither the p-value from TOST
  nor the SGPV are measures of \enquote{evidence} - we fully agree with
  BLume et al., 2018, in this respect). We also do not say the p-value
  is \enquote{naturally informative}. Indeed, related to point 3 above,
  we tried to be consistent in interpreting the TOST procedure from a
  Neyman-Pearson perspective, and focus on error control. So we
  regrettably do not know how to incorporate this point.
\item
  We fully agree with the reviewer on point 5 that \enquote{The maximum
  Type I Error rate for the SGPV over the null interval is 5\%, exactly
  like the TOST test.} Indeed, given the direct overlap between the TOST
  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
  1 and 0, any error rates (when concluding support for the null or
  alternative when the SGPV is either 1 or 0) must be identical. This is
  why we were so surprised when Blume et al (2018) write \enquote{They
  control the Type I error naturally, forcing it to zero as the sample
  size grows. This, in turn, offsets Type I Error inflation that results
  from multiple comparisons or multiple examinations of accumulating
  data. Findings identified by second-generation p-values are less
  likely to be false discoveries than findings identified by classical
  p-values. Consequently, second-generation p-values do not require
  ad-hoc adjustments to provide strict error control and this improves
  power in studies with massive multiple comparisons.} Clearly, it can
  not both be true that the the error rate of SGPV and TOST is
  identical, TOST requires adjusting for multiple comparisons, but the
  SGPV does not.
\end{enumerate}

The editor asks us to better substantiate the frequency claims for the
comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value
are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1)
we do not think any additional substantiation is possible, especially
since the reviewer agrees that (as long as confidence intervals are used
to calculate the SGPV, which we now clearly limit our conclusions to)
\enquote{The maximum Type I Error rate for the SGPV over the null
interval is 5\%, exactly like the TOST test}.

Nevertheless, we agree this discussion was a bit too extensive. Given my
own fondness of error control in statistical inferences, I get worried
if researchers suggest we can ignore it, especially when making multiple
comparisons. Imagine people start to use the SGPV instead of the TOST
procedure whenever they perform 20 tests, and then argue they do not
need to correct for multiple comparison - I think we can all agree this
is undesireable! We have reduced the two paragraphs to one hopefully
clear statement about the need to control error rates, also when using
the SGPV. We hope this addresses the concerns by the editor as well as
the reviewer, while still making an important point in the literature
about the need to control error rates (if one cares about drawing
incorrect conclusions).

Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
\enquote{Adjustments for multiple comparisons are obviated} (p.~15).
However, this is not correct. Given the direct relationship between TOST
and SGPV highlighted in this manuscript (where to TOST \emph{p} = 0.025
equals SGPV = 1, as long as the SGPV is calculated based on confidence
intervals, and assuming continuous and normally distributed data), not
correcting for multiple comparisons will inflate the probability of
concluding the absence of a meaningful effect based on the SGPV in
exactly the same way as for equivalence tests. Whenever statistical
tests are interpreted as support for a hypothesis (e.g., SPGV = 0 or
SGPV =1), it is possible do so erroneously, and if researchers want to
control error rates, they need to correct for multiple comparisons.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\item
  We have removed this section while addressing point 5 above, and thus
  incorporated the reviewers'suggestion to remove these statements.
\item
  We have not removed the paragraph about multiple comparisons, as the
  reviewer asks, but we have simplified our treatment of it. We do not
  need any other argument to make our claims about multiple comparisons
  that fact, noted by the reviewer, that \enquote{The maximum Type I
  Error rate for the SGPV over the null interval is 5\%, exactly like
  the TOST test.} This is true, and it logically follows (hence, no
  mathematical proof is needed) that error rates need to be controlled
  when using SGPV to conclude support for the null-hypothesis. We blieve
  error control is important enough to include this paragraph in the
  paper, as we believe that lack of error control was one of the causes
  of the replication crisis in psychology.
\item
  We thank the reviewer for this comment. Indeed, to calculate
  confidence intervals around a correlation, the Fisher's
  z-transformation is used, which is approximately normally distributed,
  and symmatric CI are calculated. When transforming these confidence
  intervals back to correlations, they become asymmetric. We have added
  to the text: \enquote{Note that calculating confidence intervals for a
  correlation involves a Fisher's z-transformation, which transforms
  values such that they are approximately normally distributed, which
  allows one to compute symmetric confidence intervals, which are then
  retransformed into a correlation, where the confidence intervals are
  asymmetric if the correlation is not exactly zero.} This is simply one
  example of a general effect mentioned in Blume et al (2018), which we
  already cited in the main text: \enquote{The magnitude of an
  inconclusive second-generation \emph{p}-value can vary slightly when
  the effect size scale is transformed. However definitive findings,
  i.e.~a \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.}
\end{enumerate}

Minor Concerns:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We added \enquote{,or more extreme data,}
\item
  This text was deleted (see major point 5 above)
\item
  We see how \enquote{reverse the SGPV} might have been confusing. We
  did not mean to imply to reverse the null and alternative. We now just
  say that we plot 1-SGPV (which is what we incorrectly tried to express
  with \enquote{reverse}).
\item
  The issue of the SGPV needing a \enquote{correction} by setting it to
  0.5 is not related to the fact that large \emph{p}-values are not
  evidence for the null. The \emph{p}-value is behaving as it is
  intended to, without any correction. A high p-value is not a
  \enquote{misleading result} - although it can be misinterpreted (which
  is exactly what we try to prevent with our work on equivalence
  testing). We therefore did not incorporate this point.
\item
  In line with comments by reviewer 1, we removed statemetns about SGPV
  not being inferential, thereby solving the issue reviewer 2 raised.
\item
  In line with major point 8, we added information that asymmetric
  condifence intervals around a correlation are symmetric when Fisher
  z-transformed. This is just an example of what Blume et al (2018)
  refer to when they write \enquote{The magnitude of an inconclusive
  second-generation \emph{p}-value can vary slightly when the effect
  size scale is transformed. However definitive findings, i.e.~a
  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.} We beieve this section, although the most detailed, is
  interesting, even only for more expert readers (indeed, Reviewer 1
  notes that \enquote{The asymmetric CI case is very interesting}). We
  have made our point less general, now only talking about correlations,
  by changing the title of this section into \enquote{The relation
  between equivalence tests and SGPV for asymmetrical confidence
  intervals around correlations}. The reviewer is correct confidence
  intervals can be created in many difference ways (e.g., with holes in
  the middle), but for this paper, we just focus on one specific case
  now, which we believe might be closest to what researchers would use
  in real life, the confidence interval around a correlation.
\item
  It is a well-known fact that the TOST can have 0 power (and indeed,
  this is one of the main issues in the Perlman and Wu (1999) paper the
  reviewer cited). As explained in Lakens (2017): \enquote{It is
  important to take statistical power into account when determining the
  equivalence bounds because, in small samples (where CIs are wide), a
  study might have no statistical power (i.e., the CI will always be so
  wide that it is necessarily wider than the equivalence bounds).} We
  agree with the reviewer it is not interesting to do a test if you have
  0 power. People should design informative experiments by doing an
  a-priori power analysis. Any problem in this respect is not a problem
  with equivalence tests, but a problem with designing a bad study. Not
  that the exact same issue applies to the SGPV. It is also possible to
  have 0 power for the SGPV - so we do not understand why the reviewer
  is so surprised about this. The question \enquote{Why use the TOST
  test then?} equally applies to \enquote{Why use the SGPV then?} if
  you, from the outset, know that the \enquote{small sample correction}
  will lead to a SGPV of 0.5.
\item
  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an
  estimate to some value. Regardless of how correction factors are
  applied in statistics, we are trying to educate our readers about what
  the \enquote{small sample correction} does. We believe our readers
  will associate \enquote{correction} with \enquote{correcting}, and
  want to explain that the SGPV is not set to a \enquote{correct} value.
  We are not talking about statistical terms here - we are warning the
  reader to not interpret \enquote{correction} in terms of normal
  language use. This is similar to warning readers that
  \enquote{significant} does not have the normal language connotation of
  \enquote{important}. We have therefore kept our original sentence.
\end{enumerate}

As a final comment, altough not explicitly listed as a major point of
minor point, we are happy to respond to the reviewers' suggestion that
Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
best summary of this discussion (of which Perlman \& Wu is one
contribution) can be found in Meyners (2012), which we cited. The
discussion has different arguments, and Meyners draws the conclusion
that there is no universially preferred approach. The power benefits of
alternative approaches are typically modest, or only noticeable in
situations where all alternatives are underpowered. The power issue is
not that important - the main discussion is about whether equivalence
tests should have a bounded rejection region, ike TOST, or an unbounded
rejection region. It might be useful to note that TOST and SGPV are
similar in this respect - both have bounded rejection regions, and if
the reviewer agrees with Perlman and Wu (1999) in the criticism against
TOST, the same criticism applies to the SGPV. If the reviewer reads
Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
an argument to ban the SGPV. We agree with Meyners, who writes:
\enquote{The debate has been quite heated in times; this section intends
to give a brief overview of the debate. We would like to emphasize again
that the differences between the approaches are minor and to a large
extent of academic interest only, as is this debate.} and concludes:
\enquote{To summarize, there is no right or wrong in most of the
arguments; the two opposing parties rather apply different criteria to
select the most appropriate test, one group focusing rather on
mathematical/statistical criteria, the other one more on
interpretability and reasonability.} We have added a reference to this
discussion for the interested reader, and added \enquote{For an
excellent discussion of the strengths and weaknesses of different
frequentist equivalence tests, including alternatives to the TOST
procedure, see Meyners, 2012.}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-blume_second-generation_2018}{}
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
(2018). Second-generation p-values: Improved rigor, reproducibility, \&
transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
e0188299.
doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\endgroup

\end{document}
